### 2018-04-01 concepts.tex
more on ddmin

In \emph{monotonic} cases, removing a part of a test cannot
increase the probability of a predicate holding.  This is fairly
common.  In these cases, when use a reduction algorithm to reduce $t$
to $r$, $P(p(r) \leq P(p(t))$.  In \emph{non-monotonic} cases,
however, there is no such upper bound.  Removing a step in $R$

@@

>>>>

Two purposes:  one is simply the usual purpose of test reduction: shrinking the test to make debugging
easier; however, the other purpose is \emph{changing the probability of failure.}

In \emph{monotonic} cases, removing a part of a test cannot
increase the probability of a predicate holding.  This is fairly
common.  In these cases, when we use a reduction algorithm to reduce $t$
to $r$, $P(p(r) \leq P(p(t))$.  In \emph{non-monotonic} cases,
however, there is no such upper bound.  Removing a step in $t$ may
increase the probability that $t$ behaves nondeterministically.

@@

The key changes required to standard delta-debugging implementations
are simply removal of some ``sanity checks'' in the code:  first, many
implementations (including the Python code provided by Zeller) assert
that the predicate holds on the original test.  In probabilistic
settings, this may not be true, and we may even be trying to find a
subset where a predicate that is very far from holding on the original
holds (a non-monotonic case where we aim to increase the probability
of nondeterminism).
